---
author: "Prashant Kalvapalle"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document:
    theme: flatly
    toc: TRUE
    toc_float: TRUE
---
  
---
title: `r title_name`
---
  
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 7, fig.height = 4)

```

## Plotting

### Raw growth curves

Interactive plot
_Try to Zoom, Select desired subcategories etc._

```{r plotrawinteract}

plotly::ggplotly(plt.raw) %>% 
  plotly::style(textposition = 'top right')

```

Static plot

```{r plotraw}

plt.raw

```


### Summary growth curves


Interactive plot
_Points showing the mean of independent replicates, line connecting the means; Light curves showing the upper and lower standard deviations_

```{r summinteract}

plotly::ggplotly(plt.summary) %>% 
  plotly::style(textposition = 'top right')

```

Static plot
_Points showing the mean of independent replicates, line connecting the means and shaded region showing standard deviations_


```{r summ}

plt.summary.directlabels

```

check for processed data as a csv file in the `/plate reader data/processed` folder