---
title: "Plate reader plotting : S015c"
author: "Prashant"
date: "June 2, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F, fig.width = 14/3, fig.height = 11.34/3)
source('./general_functions_plate_reading.R')
```

## User inputs


User inputs for multiple sheets

```{r input data, message=F, results='hide'}
# User inputs: 1. Enter name of the excel file, 2. Name of the data sheet(S) 3. number of rows and columns in plate reader data 4. Title for plots #comment (file name starts in the previous directory of this Rproject)

flnm <- 'S015c_AHL flip timecourse_3-7-19'

flpath <- str_c('../',flnm,'.xlsx')
fl <- read_plateReader_file(flpath) # load all non empty sheets of the excel file into fl - as a list 
sheet_names <- c("0 hr","6 hr","24 hr", "48 hr") # list the sheets to be loaded
n_Rows <- 8; 
n_Cols <- 12; 
# check the number of rows and columns for first sheet listed below
plotting_order <- c("pRV01 ","pPK7/8 ", "pPK7/17 ","pSH001 ",'rGFP','fGFP')
```

## Data crunching

Copy the tables of GFP, OD, Sample names etc. in excel and run the command below to get it into R
Doing calculations with the tables, relating sample names with the values

```{r data analysis}
table_c0 <- extract_from_given_sheet(sheet_names[1], 3, 12) %>% mutate(Time = 0) # extracing from each sheet
table_c1 <- extract_from_given_sheet(sheet_names[2], n_Rows, n_Cols) %>% mutate(Time = 6)
table_c2 <- extract_from_given_sheet(sheet_names[3], n_Rows, n_Cols) %>% mutate(Time = 24)
table_c3 <- extract_from_given_sheet(sheet_names[4], 3, 12) %>% mutate(Time = 48)

all_days_table <- bind_rows(table_c0,table_c1,table_c2,table_c3) # merge all sheets into 1 table

all_days_table %<>% arrange(Inducer, Samples) %>% mutate(Samples = fct_inorder(Samples)) # arranging samples again to make up for factor mismatch
all_days_table$Samples %<>% fct_relevel(plotting_order) # manually reorder sample order for plotting

all_days_gathered <- all_days_table %>% gather(key = 'Measurement', value = 'Reading', OD, GFP, RFP, 'GFP/RFP', 'GFP/OD', 'RFP/OD') # gather different measurements and ratios into 1 column

```

## Data tables

Showing raw data and processed data here 

GFP/RFP values
``` {r}
# Not showing anything for now # format with colours etc for good visualization
```


## Plotting

Plotting GFP/RFP : mean and sd

```{r plotting1}
sel_table1 <- all_days_table %>% group_and_summarize_at() %>% filter(!str_detect(Samples, "MG|LB")) %>% filter(!str_detect(Inducer, "s")) # filter neccesary samples for plotting ; by default mean and variance of GFP/RFP column

plt1 <- ggplot(sel_table1, aes(Time, mean, shape = Inducer)) + geom_point(size = 2) +  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width = 0.25) + facet_wrap(~ Samples) + geom_line() + scale_shape_manual(values = c(1,19)) + scale_x_continuous(breaks = c(0,6,24,48)) + ylab('GFP/RFP (a.u.)') + ggtitle('AHL flipping with time') + labs(colour = '[AHL]')
plt2 <- plt1 %>% format_classic() %>% format_logscale()
plt2
# ggsave('plots and data/S015_linear.png', plt1)
# ggsave('plots and data/test.png', width = 14/3, height = 11.34/3)
```
Plotting GFP : mean and sd

```{r plotting5}
sel_table1 <- all_days_table %>% group_and_summarize_at('GFP/OD') %>% filter(!str_detect(Samples, "MG|LB")) %>% filter(!str_detect(Inducer, "s")) # filter neccesary samples for plotting ; by default mean and variance of GFP/RFP column

plt9 <- ggplot(sel_table1, aes(Time, mean, shape = Inducer)) + geom_point(size = 2) +  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width = 0.25) + facet_wrap(~ Samples) + geom_line() + scale_shape_manual(values = c(1,19)) +  scale_x_continuous(breaks = c(0,6,24,48)) + ylab('GFP/OD (a.u.)') + ggtitle('AHL flipping with time') + labs(colour = '[AHL]')
plt10 <- plt9 %>% format_classic() %>% format_logscale()
plt10
```

Plotting GFP/OD and RFP/OD: mean and SD

```{r plotting4}
sel_table4 <- all_days_table %>% group_and_summarize_at(c('GFP/OD','RFP/OD')) %>% filter(!str_detect(Samples, "LB|MG")) %>% filter(!str_detect(Inducer, "s")) # filter neccesary samples for plotting ; by default mean and variance of GFP/RFP column
sel_table4_gathered <- sel_table4 %>% gather(key = 'Measurement', value = 'Reading', -Samples, -Inducer, -Time) %>% separate(Measurement, into = c('Measurement','val'),"_") %>% spread(val,Reading) # Seperate mean and variance and group by variable of measurement

plt7 <- ggplot(sel_table4_gathered, aes(Time, mean, colour = Measurement, shape = Inducer)) + geom_point(size = 2) +  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width = 0.25) + facet_wrap(~ Samples) + geom_line() + scale_shape_manual(values = c(1,19)) + scale_x_continuous(breaks = c(0,6,24,48)) + ylab('Fluorescence/OD (a.u.)') + xlab('Time (hr)') + ggtitle('AHL flipping with time') 
plt8 <- plt7 %>% format_classic()
plt8 #+ scale_colour_manual(values = c('#4daf4a' ,'#e41a1c'))
```

Plotting OD : mean and SD

```{r plotting3}
sel_table3 <- all_days_table %>% group_and_summarize_at('OD') %>% filter(!str_detect(Samples, "LB")) %>% filter(!str_detect(Inducer, "s")) # filter neccesary samples for plotting ; by default mean and variance of GFP/RFP column

plt5 <- ggplot(sel_table3, aes(Time, mean, colour = Inducer)) + geom_point(size = 1) +  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width = 0.25) + facet_wrap(~ Samples) + geom_line() + scale_x_continuous(breaks = c(0,6,24,48)) + ylab('OD') + ggtitle('AHL flipping with time') 
plt6 <- plt5 %>% format_classic()
plt6
```

Plotting all GFP/OD and RFP/OD (individual replicates)

```{r plotting2}
sel_table2 <- all_days_gathered %>% filter(str_detect(Measurement,"^GFP/OD|^RFP/")) %>% filter(!str_detect(Samples, "LB|MG")) %>% filter(!str_detect(Inducer, "s")) # filter neccesary samples for plotting

plt3 <- ggplot(sel_table2, aes(Time, Reading, colour = Measurement, shape = Inducer, group = interaction(Inducer, Measurement, `Replicate #`))) + geom_line() + geom_point(size = 2) + scale_shape_manual(values = c(1,19)) + facet_wrap(~Samples, scales = 'fixed') +  scale_x_continuous(breaks = c(0,6,24,48)) + ylab('Fluorescence/OD (a.u.)') + ggtitle('AHL flipping with time') 
plt4 <- plt3 %>% format_classic() # %>% format_logscale()
plt4 #+ scale_colour_manual(values = c('#4daf4a' ,'#e41a1c'))
# ggsave('plots and data/S015_linear.png', plt1)
# ggsave('plots and data/test.png', width = 14/3, height = 11.34/3)
```
