---
title: "RBS library : S011b"
author: "Prashant"
date: "July 29, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F, fig.width = 14, fig.height = 3.5)
source('./general_functions_plate_reading.R')
```

## User inputs


User inputs for multiple sheets

```{r input data, message=F, results='hide'}
# User inputs: 1. Enter name of the excel file, 2. Name of the data sheet(S) 3. number of rows and columns in plate reader data 4. Title for plots #comment (file name starts in the previous directory of this Rproject)

flnm <- 'S011b_RBS library2_25-7-19'

flpath <- str_c('../',flnm,'.xlsx')
fl <- read_plateReader_file(flpath) # load all non empty sheets of the excel file into fl - as a list 
sheet_names <- c( "day0","d1.u","d1.i","d2.u","d2.i") # list the sheets to be loaded
n_Rows <- 8; 
n_Cols <- 12; 
# check the number of rows and columns for first sheet listed below
```

## Data crunching

Copy the tables of GFP, OD, Sample names etc. in excel and run the command below to get it into R
Doing calculations with the tables, relating sample names with the values

```{r data analysis}
table_c0 <- extract_from_given_sheet(sheet_names[1], 8, 12) %>% mutate(Inducer = '0 uM') %>% mutate(Day = '0') # extracing from each sheet
table_c1 <- extract_from_given_sheet(sheet_names[2], n_Rows, n_Cols) %>% mutate(Inducer = '0 uM') %>% mutate(Day = '1')
table_c2 <- extract_from_given_sheet(sheet_names[3], n_Rows, n_Cols) %>% mutate(Inducer = '1 uM') %>% mutate(Day = '1')
table_c3 <- extract_from_given_sheet(sheet_names[4], n_Rows, n_Cols) %>% mutate(Inducer = '0 uM') %>% mutate(Day = '2')
table_c4 <- extract_from_given_sheet(sheet_names[5], n_Rows, n_Cols) %>% mutate(Inducer = '1 uM') %>% mutate(Day = '2')

merged2 <- bind_rows(table_c0,table_c1,table_c2) # merge all sheets into 1 table

all_days_table <- merged2 %>% separate(Samples, into = c('category', NA), sep = '\\.', remove = F) %>% mutate(category  = fct_lump(category, 2, other_level = 'Controls')) # create a category row for controls and the library clones 6 and 7

# determine plotting order: based on ascending order of GFP/OD values (for single replicate data)
plotting_order <- all_days_table %>% filter(str_detect(Inducer,'0') & str_detect(Day,'1')) %>% arrange(`GFP/OD`) %>%  mutate(Samples = fct_inorder(Samples)) %>% pull(Samples) %>% levels()

all_days_table$Samples %<>% fct_relevel(plotting_order) # manually reorder samples for plotting

all_days_gathered <- all_days_table %>% gather(key = 'Measurement', value = 'Reading', OD, GFP, RFP, 'GFP/RFP', 'GFP/OD', 'RFP/OD') # gather different measurements and ratios into 1 column

```

## Data tables

Showing raw data and processed data here 

GFP/RFP values
``` {r}
# Not showing anything for now # format with colours etc for good visualization
```


## Plotting


Plotting GFP/OD

```{r plotting2}
sel_table2 <- all_days_table %>% group_and_summarize_at('GFP/OD') #%>% filter(!str_detect(Samples, "MG|LB")) %>% filter(!str_detect(Inducer, "s")) # filter neccesary samples for plotting ; by default mean and variance of GFP/RFP column
WT_baseline = sel_table2 %>% filter(str_detect(Inducer,'0') & str_detect(Day,'1') & str_detect(Samples,'RV')) %>% pull(mean) # find the value for pRV01

plt3 <- plot_mean_facetted(sel_table2) + ylab('GFP/OD (a.u.)') + geom_hline(yintercept = WT_baseline, linetype = 2) # plot the mean, add y axis label and a baseline indication
plt4 <- plt3 %>% format_classic() %>% format_logscale()
plt4
```

Merge all GFP/OD

```{r plotting3}
# plotting GFP/OD without facetting, includes a reference line for the WT control

plt5 <- ggplot(sel_table2, aes(Samples, mean, colour = Day, shape = Inducer)) + geom_point(size = 2) + scale_shape_manual(values = c(1,19)) + ylab('GFP/OD (a.u.)') + ggtitle('RBS mutant library-2') + geom_hline(yintercept = WT_baseline, linetype = 2)
plt6 <- plt5 %>% format_classic() %>% format_logscale()
plt6
```

Plotting GFP/RFP 

```{r plotting1}
sel_table1 <- all_days_table %>% group_and_summarize_at() #%>% filter(!str_detect(Samples, "MG|LB")) %>% filter(!str_detect(Inducer, "s")) # filter neccesary samples for plotting ; by default mean and variance of GFP/RFP column

plt1 <- plot_mean_facetted(sel_table1) + ylab('GFP/RFP (a.u.)') # plot the mean and add y axis label
plt2 <- plt1 %>% format_classic() %>% format_logscale() # formatting with clean classic look and on a logscale
plt2

```

Plotting OD 

```{r plotting5}
sel_table5 <- all_days_table %>% group_and_summarize_at('OD') # filter neccesary samples for plotting ; by default mean and variance of GFP/RFP column

plt9 <- plot_mean_facetted(sel_table5) + ylab('OD')  # plot the mean and add y axis label 
plt10 <- plt9 %>% format_classic()
plt10
```

Plotting GFP/OD and RFP/OD

```{r plotting4}
sel_table4 <- all_days_table %>% group_and_summarize_at(c('GFP/OD','RFP/OD')) %>% filter(str_detect(Day,'1')) #%>% arrange(Inducer, Measurement, mean) %>% ungroup() %>%  mutate(Samples = fct_inorder(Samples)) # arrange samples in ascending order of uninduced # filter neccesary samples for plotting ; by default mean and variance of GFP/RFP column

plt7 <- ggplot(sel_table4, aes(Samples, mean, colour = Measurement, shape = Inducer)) + geom_point(size = 2) + scale_shape_manual(values = c(1,19,2)) + facet_grid(~ category, scales = 'free_x', space = 'free_x') + ylab('Fluorescence/OD (a.u.)') + ggtitle('RBS mutant library-2 (Day1)')
plt8 <- plt7 %>% format_classic() %>% format_logscale()
plt8 #+ scale_colour_manual(values = c('#4daf4a' ,'#e41a1c'))
```

Fold change induced vs uninduced GFP/OD

```{r plotting6}
sel_table6 <- all_days_table %>% select(Samples, category, Inducer, Day, `GFP/OD`) %>% filter(str_detect(Day, '1')) %>% spread(Inducer, `GFP/OD`) %>% mutate(ratio = `1 uM`/`0 uM`) # spread GFP/OD for induced and uninduced and calculate ratio
sel_table6$Samples %<>%  fct_relevel(plotting_order)

plt11 <- ggplot(sel_table6, aes(Samples, ratio)) + geom_point(size = 2) + facet_grid(~ category, scales = 'free_x', space = 'free_x') + geom_hline(yintercept = 1, linetype = 2) + ylab('Induced/Uninduced ratio (GFP/OD)') + ggtitle('RBS mutant library-2 (Day 1)')
plt12 <- plt11 %>% format_classic()
plt12
```

Fold change induced vs uninduced GFP/OD : In logscale

```{r plotting7}

plt13 <- plt12 %>% format_logscale()
plt13
```

Selected members with GFP/OD induced > uninduced: combined plot

```{r plotting8}
samples_increase_induction <- sel_table6 %>% filter(ratio > 1) %>% pull(Samples) # select the samples with induced GFP/OD > uninduced
samples_lower_baseline <- sel_table2 %>% filter(str_detect(Day, '1') & str_detect(Inducer, '0')) %>% filter(mean <= WT_baseline) %>% pull(Samples) # select the samples with induced GFP/OD > uninduced

sel_table7 <- sel_table4 %>% filter(Samples %in% samples_increase_induction & Samples %in% samples_lower_baseline) # select samples with lower baseline and increased GFP/OD upon induction on day1

plt14 <- ggplot(sel_table7, aes(Samples, mean, colour = Measurement, shape = Inducer)) + geom_point(size = 2) + scale_shape_manual(values = c(1,19,2)) + ylab('Fluorescence/OD (a.u.)') + ggtitle('RBS mutant library-2 (Day1): Selected clones') + geom_hline(yintercept = WT_baseline, linetype = 2)
plt15 <- plt14 %>% format_classic() %>% format_logscale()
plt15
```

Selected members with GFP/OD induced > uninduced 

```{r plotting9}

plt15 + facet_grid(~ category, scales = 'free_x', space = 'free_x')
```